### 2020-06-04 README.Rmd
working on README

```{r, eval = run_bw}
tic()
focal_vs_comp_bw <- bw_growth_df %>% 
  create_focal_vs_comp(max_dist, model_specs = bw_specs, cv_grid = bw_cv_grid, id = "treeID")
toc()
```

>>>>

```{r, eval = run_bw}
if (!file.exists("focal_vs_comp_bw.Rdata")) {
  tic()
  focal_vs_comp_bw <- bw_growth_df %>% 
    create_focal_vs_comp(max_dist, model_specs = bw_specs, cv_grid = bw_cv_grid, id = "treeID")
  toc()
} else {
  load("focal_vs_comp_bw.Rdata)
}
```
